### 2022-11-13 NSF2022/Description/backgroundv3.tex
yny 1113d

Having a non-specific model that replicates physical details
is the crown jewel of applied mathematics.
\emph{Further applications} include
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\begin{wrapfigure}[9]{l}{2.1in}
  \vspace{-5pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

@@

Regarding mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.

>>>>

%Having a non-specific model that replicates physical details
%is the crown jewel of applied mathematics.
The mathematical framework in equations~\eqref{eq:RBT}--\eqref{eqn:stressbalance}
are highly desirable from the applied math point of view as there are many
\emph{Further Applications}, such as
(i) amphiphilic Janus spheres that form diverse suprastructures
\cite{HaBr20,McBr21,Bradley2017},
(ii) pickering emulsions involving
two-phase fluids and dense suspensions \cite{Bradley2016},
(iii) creation and manipulation of small droplets
using amphiphilic microparticles \cite{Ha2022SurfaceEM,Ha2020MinimalSC},
and (iv) tension drivent fabrication of microstructures
~\cite{Dasgupta2017, Leong2007, Reynolds2019, Cho2010,Zeng20223DprintedMT,Russell2016EnergyLF}.
\begin{wrapfigure}[9]{l}{2.1in}
  \vspace{-5pt}
  \centering
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutFEM.pdf}
  \includegraphics[width=1in]{figures/Background/Peanut/PeanutIE.pdf}
  \caption{\label{fig:fem_vs_bie} \footnotesize A finite element method
  ({\em left}) requires meshing the entire domain (typically into
  triangles), while a BIE ({\em right}) requires meshing only the
  boundary of the domain.}
\end{wrapfigure}

@@

Regarding the mathematical motivation for~\eqref{eq:RBT}--\eqref{eqn:stressbalance},
when equation \eqref{eqn:phase} takes the form of a screened Laplace equation
$-\epsilon^2 \Delta \phi + \phi =0$, for a fixed domain $\Omega$ with
smooth boundary, if the material label $h_i = 1$
everywhere, then $\phi$ has a boundary layer going from $1$ at the
boundary to $0$ in the bulk and one can prove that 
$\lim_{\epsilon \to 0} E = \frac{1}{2}\gamma |\partial \Omega|$.
In other words, 
interfacial energy enters the problem even in the linear case,
\emph{because of the introduction of granule boundaries.}
We are confident
that~\eqref{eq:RBT}--\eqref{eqn:stressbalance} is a correct description
of long-range interactions between granule surfaces.
